Title Goes Here

### 2017-10-03 analysis/paper/paper.Rmd
added kinds of output
nmeth csl

---
title: "Title Goes Here"
author:
  - Robrecht Cannoodt
  - Wouter Saelens
  - Helena Todorov
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
    fig_caption: yes
    reference_docx: templates/template.docx
bibliography: references.bib
csl: journal-of-archaeological-science.csl
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

>>>>

---
title: "Title Goes Here"
author:
  - Robrecht Cannoodt
  - Wouter Saelens
  - Helena Todorov
  - Yvan Saeys
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
    fig_caption: yes
    reference_docx: templates/template.docx
bibliography: references.bib
csl: nature-methods.csl
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

*Points to maybe raise*:
- Some methods can handle different trajectories which are not directly described in the main paper: eg. circular trajectories (for a lot of principal curves algorithms using `periodic.lowess`), trees (for a lot of bifurcation methods)
